### 2024-04-07 author-kit-CVPR2024-v2/sec/1_intro.tex
updated

In recent years, dance has surged in popularity, whether through TikTok trends in younger 
generations, the growing fanbase for elaborate K-pop dance videos, or the performances in 
reality competition shows (which themselves cover wide genres from ballet and contemporary 
to ballroom dances). As a result of this growing interest, many eager dance novices have 
attempted to self-teach from the abundant dance videos online, available through a variety 
of platforms. However, such individuals often struggle with breaking down movements due to 
the speed or intricacy with which they were executed.

We aim to use Computer Vision to partition dance movements into more easily digestible chunks 
by creating a model that can learn (vectorize) dance choreography from a given dance video, and 
output it in a more human-readable form, such as by describing multiple steps in a motion and 
adding counts or timings for context. By developing a tool that provides detailed descriptions 
of human positions and gestures alongside counts or musical beats, learning dance choreographies 
could become much more accessible and approachable for a broader audience.

%-------------------------------------------------------------------------
\subsection{Existing Attempts}
Several existing attempts have been made to tackle the challenge of learning dance from online 
videos, each with its own approach and limitations. One such approach involves platforms that 
generate reskinned versions of dance performances, offering visual references for users. These 
platforms overlay graphics or animations onto the original video, highlighting key movements or 
positions to provide guidance. While these reskinned versions serve as visual aids, they 
typically do not offer active instruction or detailed breakdowns of the dance steps. As a result, 
users may struggle to fully grasp the nuances and intricacies of the movements, limiting the 
effectiveness of this approach as a learning tool.

Another example is a DancePal Hackathon project, which adopts a more technical approach by 
comparing an ideal video with the end user's video skeletons. This method involves analyzing the 
skeletal poses extracted from both videos and identifying discrepancies between them. While this 
approach has the potential to provide personalized feedback to users based on their own performances, 
it comes with several challenges. Firstly, it requires an ideal video with specific lighting, 
background, and perspective conditions to serve as a reference, which may not always be feasible 
to obtain. Additionally, accurately mapping movements onto predefined definitions can be difficult, 
especially for complex dance sequences with varying styles and interpretations. As a result, the 
effectiveness of this approach may be limited by the availability of suitable reference videos and 
the accuracy of the mapping process.

Unlike reskinned versions of dance performances, our proposed method provides detailed instructional 
breakdowns of dance movements, guiding learners through each step with clarity and precision. This 
active instruction facilitates better understanding and retention of choreography. Additionally, our 
method could be expanded to offer personalized feedback based on the analysis of the learner's own 
video and that of an original dance video, ideally without the requirement for perfect lighting or 
camera angle conditions.

\subsection{Useful Techniques}
Several computer vision techniques offer promising avenues for addressing the challenge of learning 
dance from online videos by providing deeper insights into the dynamics and nuances of dance 
movements. One such technique involves exploring 3D models instead of traditional 2D skeletonization
 methods to create more comprehensive representations of dance movements. Unlike 2D skeletonization, 
 which captures only the spatial coordinates of key body joints in a single plane, 3D modeling 
 techniques can capture the full spatial extent of movements, including depth information. This 
 allows for a more accurate and detailed representation of the dancer's body and movements in 
 three-dimensional space, which is particularly valuable for capturing complex and multi-dimensional 
 dance choreographies.

 In addition to 3D modeling, other computer vision techniques such as action recognition, pose 
estimation, trajectory analysis, and video segmentation and tracking can provide valuable insights 
into the dynamics of dance movements. Action recognition algorithms can automatically identify and 
classify different dance gestures and sequences, allowing for automated analysis of choreographic 
patterns and styles. Pose estimation techniques can accurately estimate the skeletal poses of 
dancers from video frames, providing a structural representation of their movements that can be 
used for further analysis and interpretation.

Trajectory analysis techniques can track the trajectories of specific body parts or movements 
over time, allowing for the analysis of movement patterns, velocities, and accelerations. This 
can provide valuable insights into the rhythmic and dynamic aspects of dance performances, 
helping learners to better understand the timing and pacing of movements. Video segmentation and 
tracking methods can segment dance videos into individual sequences or movements, allowing for more 
focused analysis and comparison of specific choreographic elements.

By leveraging these advanced computer vision techniques, learners can gain a deeper understanding 
of the dynamics and nuances of dance movements, facilitating more effective learning experiences. 
These techniques can help learners to break down complex choreographies into smaller, more 
manageable components, identify areas for improvement, and refine their technique with greater 
precision and accuracy. Overall, the integration of computer vision into dance learning has the 
potential to revolutionize the way dance is taught and learned, making it more accessible, engaging, 
and effective for dancers of all levels.

\subsection{Challenges}
Several challenges arise from attempting this project. One is the quality of input data, which 
encompasses various factors such as lighting, angles, occlusions, frame rates, and blurring. These 
factors can significantly impact the accuracy of movement analysis, as they can obscure or distort 
key visual information needed for understanding dance movements. Addressing these challenges may 
require the development of robust computer vision algorithms capable of handling noisy or low-quality 
video data, as well as techniques for preprocessing and enhancing the visual information to improve 
analysis accuracy.

Moreover, handling interactions between multiple dancers in an ideal video presents additional 
complexities in accurately capturing and representing dance movements. In many dance performances, 
especially group or partner dances, dancers may interact with each other in complex ways, such as 
lifts, partner work, or coordinated movements. Capturing these interactions and accurately 
representing them in the analysis poses challenges for computer vision algorithms, as they must be 
able to differentiate between individual dancers and track their movements independently while also 
accounting for their interactions with others. Addressing this challenge may require the development 
of advanced tracking and segmentation techniques capable of accurately identifying and tracking 
multiple dancers in a crowded or dynamic environment.

Overall, addressing these challenges requires a multidisciplinary approach that combines expertise 
in computer vision, dance analysis, and human-computer interaction. By developing robust algorithms, 
incorporating domain-specific knowledge, and leveraging advanced techniques for handling complex 
visual data, it is possible to create a tool that effectively supports learning dance from online 
videos using computer vision. However, continued research and development efforts are needed to 
overcome these challenges and realize the full potential of computer vision technology in the 
field of dance education.\cite{Authors14b}

\subsection{Technical Gap}
The primary aim of this project is to reduce the technical gap between online dance learning resources and 
effective dance instruction. By enabling the correspondence between individuals with different body proportions 
captured from various angles, this tool seeks to enhance the accessibility and inclusivity of dance education. 
This interdisciplinary endeavor involves collaboration between experts in dance, biomechanics, and computer 
vision, with computer vision providing quantitative analysis capabilities to enhance the understanding and 
teaching of dance movements.

In conclusion, developing a tool for learning dance from online videos using computer vision holds 
great potential for revolutionizing dance education and making it more accessible to a wider 
audience. By leveraging advanced computer vision techniques and interdisciplinary collaboration, 
this project aims to bridge the gap between online dance resources and effective dance instruction, 
ultimately empowering individuals to learn and appreciate dance in new and innovative ways.

>>>>

\indent In recent years, dance has surged in popularity, whether through TikTok trends in younger 
generations, the growing fanbase for elaborate K-pop dance videos, or the performances in 
reality competition shows (which themselves cover wide genres from ballet and contemporary 
to ballroom dances). As a result of this growing interest, many eager dance novices have 
attempted to self-teach from the abundant dance videos online, available through a variety 
of platforms. However, such individuals often struggle with breaking down movements due to 
the speed or intricacy with which they were executed.
\\
\indent We aim to use Computer Vision to partition dance movements into more easily digestible chunks 
by creating a model that can learn (vectorize) dance choreography from a given dance video, and 
output it in a more human-readable form, such as by describing multiple steps in a motion and 
adding counts or timings for context. By developing a tool that provides detailed descriptions 
of human positions and gestures alongside counts or musical beats, learning dance choreographies 
could become much more accessible and approachable for a broader audience.

%-------------------------------------------------------------------------
\subsection{Existing Attempts}
\indent Several existing attempts have been made to tackle the challenge of learning dance from online 
videos, each with its own approach and limitations. One such approach involves platforms that 
generate reskinned versions of dance performances, offering visual references for users. These 
platforms overlay graphics or animations onto the original video, highlighting key movements or 
positions to provide guidance. While these reskinned versions serve as visual aids, they 
typically do not offer active instruction or detailed breakdowns of the dance steps. As a result, 
users may struggle to fully grasp the nuances and intricacies of the movements, limiting the 
effectiveness of this approach as a learning tool.
\\
\indent Another example is a DancePal Hackathon project, which adopts a more technical approach by 
comparing an ideal video with the end user's video skeletons\cite{Authors14c}. This method involves analyzing the 
skeletal poses extracted from both videos and identifying discrepancies between them. While this 
approach has the potential to provide personalized feedback to users based on their own performances, 
it comes with several challenges. Firstly, it requires an ideal video with specific lighting, 
background, and perspective conditions to serve as a reference, which may not always be feasible 
to obtain. Additionally, accurately mapping movements onto predefined definitions can be difficult, 
especially for complex dance sequences with varying styles and interpretations. As a result, the 
effectiveness of this approach may be limited by the availability of suitable reference videos and 
the accuracy of the mapping process.
\\
\indent Unlike reskinned versions of dance performances, our proposed method provides detailed instructional 
breakdowns of dance movements, guiding learners through each step with clarity and precision. This 
active instruction facilitates better understanding and retention of choreography. Additionally, our 
method could be expanded to offer personalized feedback based on the analysis of the learner's own 
video and that of an original dance video, ideally without the requirement for perfect lighting or 
camera angle conditions.

\subsection{Useful Techniques}
\indent Several computer vision techniques offer promising avenues for addressing the challenge of learning 
dance from online videos by providing deeper insights into the dynamics and nuances of dance 
movements. One such technique involves exploring 3D models instead of traditional 2D skeletonization
 methods to create more comprehensive representations of dance movements. Unlike 2D skeletonization, 
 which captures only the spatial coordinates of key body joints in a single plane, 3D modeling 
 techniques can capture the full spatial extent of movements, including depth information\cite{Alpher03}. This 
 allows for a more accurate and detailed representation of the dancer's body and movements in 
 three-dimensional space, which is particularly valuable for capturing complex and multi-dimensional 
 dance choreographies\cite{Authors14b}.
\\
\indent In addition to 3D modeling, other computer vision techniques such as action recognition, pose 
estimation, trajectory analysis, and video segmentation and tracking can provide valuable insights 
into the dynamics of dance movements. Action recognition algorithms can automatically identify and 
classify different dance gestures and sequences, allowing for automated analysis of choreographic 
patterns and styles. Pose estimation techniques can accurately estimate the skeletal poses of 
dancers from video frames, providing a structural representation of their movements that can be 
used for further analysis and interpretation.
\\
\indent Trajectory analysis techniques can track the trajectories of specific body parts or movements 
over time, allowing for the analysis of movement patterns, velocities, and accelerations\cite{Alpher02}. This 
can provide valuable insights into the rhythmic and dynamic aspects of dance performances, 
helping learners to better understand the timing and pacing of movements. Video segmentation and 
tracking methods can segment dance videos into individual sequences or movements, allowing for more 
focused analysis and comparison of specific choreographic elements.
\\
\indent By leveraging these advanced computer vision techniques, learners can gain a deeper understanding 
of the dynamics and nuances of dance movements, facilitating more effective learning experiences. 
These techniques can help learners to break down complex choreographies into smaller, more 
manageable components, identify areas for improvement, and refine their technique with greater 
precision and accuracy. Overall, the integration of computer vision into dance learning has the 
potential to revolutionize the way dance is taught and learned, making it more accessible, engaging, 
and effective for dancers of all levels.

\subsection{Challenges}
\indent Several challenges arise from attempting this project. One is the quality of input data, which 
encompasses various factors such as lighting, angles, occlusions, frame rates, and blurring. These 
factors can significantly impact the accuracy of movement analysis, as they can obscure or distort 
key visual information needed for understanding dance movements. Addressing these challenges may 
require the development of robust computer vision algorithms capable of handling noisy or low-quality 
video data, as well as techniques for preprocessing and enhancing the visual information to improve 
analysis accuracy.
\\
\indent Moreover, handling interactions between multiple dancers in an ideal video presents additional 
complexities in accurately capturing and representing dance movements. In many dance performances, 
especially group or partner dances, dancers may interact with each other in complex ways, such as 
lifts, partner work, or coordinated movements. Capturing these interactions and accurately 
representing them in the analysis poses challenges for computer vision algorithms, as they must be 
able to differentiate between individual dancers and track their movements independently while also 
accounting for their interactions with others. Addressing this challenge may require the development 
of advanced tracking and segmentation techniques capable of accurately identifying and tracking 
multiple dancers in a crowded or dynamic environment.
\\
\indent Overall, addressing these challenges requires a multidisciplinary approach that combines expertise 
in computer vision, dance analysis, and human-computer interaction. By developing robust algorithms, 
incorporating domain-specific knowledge, and leveraging advanced techniques for handling complex 
visual data, it is possible to create a tool that effectively supports learning dance from online 
videos using computer vision. However, continued research and development efforts are needed to 
overcome these challenges and realize the full potential of computer vision technology in the 
field of dance education.

\subsection{Technical Gap}
\indent The primary aim of this project is to reduce the technical gap between online dance learning resources and 
effective dance instruction. By enabling the correspondence between individuals with different body proportions 
captured from various angles, this tool seeks to enhance the accessibility and inclusivity of dance education. 
This interdisciplinary endeavor involves collaboration between experts in dance, biomechanics, and computer 
vision, with computer vision providing quantitative analysis capabilities to enhance the understanding and 
teaching of dance movements.
\\
\indent In conclusion, developing a tool for learning dance from online videos using computer vision holds 
great potential for revolutionizing dance education and making it more accessible to a wider 
audience. By leveraging advanced computer vision techniques and interdisciplinary collaboration, 
this project aims to bridge the gap between online dance resources and effective dance instruction, 
ultimately empowering individuals to learn and appreciate dance in new and innovative ways.
